---
title: "regression"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

installation_needed  <- FALSE
loading_needed       <- TRUE

package_list <- c("AER","foreign", "sandwich","ggplot2", "reshape", "boot", "zoo", 
                  "quantreg", "dummies", "stargazer", "lmtest", "plm","openxlsx", "stringr",
                  "moments",'readstata13','gmm', 'dplyr', 'tidyr','xtable', 'sem', 'bdynsys', 
                  'ivpack','fixest','modelsummary')

if(installation_needed){install.packages(package_list)}
if(loading_needed){lapply(package_list, require, character.only = TRUE)}

rm(list=ls())

dir_reg <- "/"
mpc_df <-  read.xlsx(paste0(dir_reg,"mpc.xlsx",sep=""))
gdp_df <- read.xlsx(paste0(dir_reg,"gdp.xlsx",sep=""))
gdp_fips_df <- read.xlsx(paste0(dir_reg,"gdp_fips.xlsx",sep=""))
infection_df <- read.xlsx(paste0(dir_reg,"infection.xlsx",sep=""))
small_biz_df <- read.xlsx(paste0(dir_reg,"small_biz.xlsx",sep=""))
ppp_df <- read.csv(paste0(dir_reg,"ppp_county.csv",sep=""))
```

```{r}
gdp=gdp_df
gdp$date_yw=paste0(gdp$year,str_pad(gdp$week,2,"left",pad = "0"))
gdp <- gdp %>%  mutate(Rank=rank(date_yw),RankDown=Rank-1)
gdp <- gdp %>% left_join(select(gdp,Rank,lag_gdp_wei=gdp_wei),by=c('RankDown'='Rank')
) %>% select(-Rank,-RankDown)
gdp <- gdp %>% arrange(year) %>% mutate(gdp_diff=(gdp_wei-lag_gdp_wei)/lag_gdp_wei)

ppp=ppp_df
ppp$date_yw=paste0(ppp$year,str_pad(ppp$week,2,"left",pad = "0"))
ppp$fips <- str_pad(ppp$COUNTY, 5, "left", pad = "0")
#ppp <- ppp %>% group_by(fips) %>% mutate(Rank=rank(date),RankDown=Rank-1)
#ppp <- ppp %>% left_join(select(ppp,Rank,lag_ppp=ppp,fips),by=c('RankDown'='Rank','fips')
#) %>% select(-Rank,-RankDown)
#ppp <- ppp %>% group_by(fips) %>% arrange(year,fips) %>% mutate(ppp_diff=ppp-lag_ppp)

infection=infection_df
infection$date_yw=paste0(infection$year,str_pad(infection$week,2,"left",pad = "0"))
columns <- c('new_death_rate', 'new_case_rate', 'new_death_count', 'new_case_count')
infection <- infection %>% mutate(across(columns,as.numeric))
```

```{r}
mpc=mpc_df
#mpc$positive_mpc <- mpc$mpc
#mpc$positive_mpc[mpc$mpc < 0] <- 0
#mpc$mpc[mpc$mpc < 0] <- NA
mpc <- mpc %>% mutate(mpc=mpc+abs(min(mpc)))

mpc$date_yw=paste0(mpc$year,str_pad(mpc$week,2,"left",pad = "0"))
mpc <- mpc %>% group_by(fips) %>% mutate(Rank=rank(date_yw),RankDown=Rank-1)
mpc <- mpc %>% left_join(select(mpc,Rank,lag_income_region=income_region,lag_annual_income=annual_income,lag_pop=tot_pop,fips),by=c('RankDown'='Rank','fips')
) %>% select(-Rank,-RankDown)

mpc <- mpc %>% group_by(fips) %>% arrange(year,fips) %>% mutate(income_diff=(annual_income-lag_annual_income)/lag_annual_income) %>% mutate(mpc_lag=lag(mpc))

mpc <- mpc %>% group_by(date_yw) %>% mutate(income_weight=lag_annual_income/sum(lag_annual_income,na.rm=TRUE)) %>%
mutate(weighted_income=lag_annual_income/sum(lag_annual_income,na.rm=TRUE)) %>% mutate(weighted_pop=lag_pop/sum(lag_pop,na.rm=TRUE))

# lag revenue
small_biz=small_biz_df
small_biz <- small_biz %>% group_by(fips) %>% mutate(Rank=rank(date_yw),RankDown=Rank-1)
small_biz <- small_biz %>% left_join(select(small_biz,Rank,lag_revenue=revenue_all,fips),by=c('RankDown'='Rank','fips')
) %>% select(-Rank,-RankDown)
small_biz <- small_biz %>% group_by(fips) %>% arrange(year,fips) %>% mutate(revenue_diff=revenue_all-lag_revenue) 
#small_biz[c("week","year")] <- lapply(small_biz[c("week","year")], as.numeric)
```


```{r}
# merge income to revenue data set
income_revenue_reg_df <- left_join(mpc, small_biz %>% select(revenue_diff,revenue_all,merchants_all,fips,date_yw), by = c("fips","date_yw"))
income_revenue_reg_df <- left_join(income_revenue_reg_df, ppp %>% select(ppp,fips,date_yw), by = c("fips","date_yw"))
income_revenue_reg_df <- left_join(income_revenue_reg_df, infection %>% select(new_case_rate,new_death_rate,new_case_count,new_death_count,fips,date_yw), by = c("fips","date_yw")) %>% mutate(state=substr(fips,1,2))

# merge revenue to gdp data set
revenue_gdp_reg_df <- left_join(small_biz,gdp %>% select (gdp_diff, date_yw), by= c("date_yw"))
revenue_gdp_reg_df <- right_join(mpc, revenue_gdp_reg_df %>% select(merchants_all, revenue_all,revenue_diff, gdp_diff,fips, date_yw), by= c("fips","date_yw")) %>% mutate(state=substr(fips,1,2))
revenue_gdp_reg_df <- left_join(revenue_gdp_reg_df, infection %>% select(new_case_rate,new_death_rate,new_case_count,new_death_count,fips,date_yw), by = c("fips","date_yw")) %>% mutate(state=substr(fips,1,2))

```

## Regression

Step2: elasticity of income to small business revenue

time fixed effect control for unobservables that are the same across states but varies with time (different variant of covid?). 
state fixed effect controls for unobservables that are varies across states but are constant over time (for example sentiment to state legislations, mask policies). 

for people with high MPC, the relationship between income difference and small business revenue diff is stronger?

income variability driven by extensive margin respons (unemployment rate, rather than wage change)

mpc is the same across time

```{r}
#reg <- femlm(income_diff ~ mpc*revenue_diff+mpc+revenue_diff+new_case_rate+new_death_rate+merchants_all,
#           data = income_revenue_reg, index = c("fips","date_yw"), model="within")

# clean up stuff

income_revenue_reg0 <- feols(income_diff ~ mpc_lag*revenue_diff , income_revenue_reg_df,weights=income_revenue_reg_df$weighted_income)
summary(income_revenue_reg0,'hetero')

income_revenue_reg1 <- feols(income_diff ~ new_death_rate+merchants_all+mpc_lag*revenue_diff | date_yw, income_revenue_reg_df, weights=income_revenue_reg_df$weighted_income)
summary(income_revenue_reg1,'hetero')

income_revenue_reg2 <- feols(income_diff ~ new_death_rate+merchants_all+mpc_lag*revenue_diff | fips, income_revenue_reg_df, weights=income_revenue_reg_df$weighted_income)
summary(income_revenue_reg2,'cluster')

income_revenue_reg3 <- feols(income_diff ~ new_death_rate+merchants_all+mpc_lag*revenue_diff | fips+date_yw, income_revenue_reg_df, weights=income_revenue_reg_df$weighted_income)
summary(income_revenue_reg3,'cluster')

p_income <- ggplot(income_revenue_reg_df, aes(x=income_diff)) + 
  geom_histogram()
p_rev <- ggplot(income_revenue_reg_df, aes(x=revenue_diff)) + 
  geom_histogram()

#summary(income_revenue_reg_tm,cluster=~state)

#fixedEffects = fixef(income_revenue_reg)
#summary(fixedEffects)

# calculate elasticity
# which_reg <- income_revenue_reg_weighted
which_reg <- income_revenue_reg3
income_margin_coef=coef(which_reg, 'mpc_lag:revenue_diff')
income_main_coef=rep(0, length(income_margin_coef))# coef(which_reg, 'revenue_diff')[1]
coef_df <- revenue_gdp_reg_df %>% select(fips,mpc_lag,mpc,revenue_diff,date_yw,annual_income,income_region,weighted_income)
coef_df <- coef_df %>% mutate(income_elasticity=mpc_lag*income_margin_coef+income_main_coef)

# we set the dictionary once and for all
#myDict = c("log(dist_km)" = "$\\ln (Distance)$", "(Intercept)" = "Constant")
# 1st export: we change the signif code and drop the intercept
#etable(res_multi, signifCode = c("a" = 0.01, "b" = 0.05),
#       drop = "Const", dict = myDict, file = "Estimation Tables.tex", 
#       replace = TRUE, title = "First export -- normal Standard-errors")
# 2nd export: clustered S-E + distance as the first coefficient
#etable(res_multi, cluster = ~Product, order = "Dist", 
#       dict = myDict, file = "Estimation Tables.tex", 
#       title = "Second export -- clustered standard-errors (on Product variable)")


#characteristics_reg <- feols(income_diff ~ new_case_rate+new_death_rate+black*revenue_diff+income_bracket*revenue_diff+tot_male*revenue_diff | fips+date_yw, income_revenue_reg_df)
#summary(characteristics_reg)
```

```{r}
library(zoo)
library(dplyr)
library(TTR)

iv_df<-income_revenue_reg_df
iv_df <- iv_df %>% left_join(gdp_fips_df,by='fips')
#iv_df$ppp_rescale<- iv_df$ppp/iv_df$gdp_2019
iv_df$ppp_impute <- iv_df$ppp %>% replace_na(0)

my_ema <- function(x, n) {
  tryCatch( {
    EMA(x, n)
  },
  error = function(e) {
    NA
  })
}

#iv_df <- iv_df %>%
#       arrange(fips,date_yw) %>%
#       group_by(fips) %>%
       #mutate(roll_sum = roll_sum(ppp_impute, 12, align = "right", fill = 0))
#         mutate(ppp_impute = my_ema(ppp_impute, 13))
suma = function(x) if (all(is.na(x))) x[NA_integer_] else sum(x, na.rm = TRUE)
simple_sum = function(x) sum(x,na.rm=TRUE)

iv_df <- iv_df %>%
         arrange(fips,date_yw) %>%
         group_by(fips) %>%
         #mutate(roll_sum = roll_sum(ppp_impute, 12, align = "right", fill = 0))
         mutate(ppp_impute = rollapplyr(ppp, 8, suma, partial = TRUE) )

iv_df$ppp_dummy <- iv_df$ppp_impute
iv_df$ppp_dummy[iv_df$ppp_impute > 0] <- 1
iv_df$ppp_dummy[iv_df$ppp_impute == 0] <- 0
#iv_df$ppp_dummy <- iv_df$ppp_dummy %>% replace_na(0)

iv_reg <- feols(income_diff ~ new_death_rate+merchants_all | mpc_lag*revenue_diff ~ mpc_lag*ppp_impute, iv_df,weights=iv_df$weighted_income)
summary(iv_reg)

iv_reg2 <- feols(income_diff ~ new_death_rate+merchants_all | mpc_lag*revenue_diff ~ mpc_lag*ppp_dummy, iv_df,weights=iv_df$weighted_income)
summary(iv_reg2)

iv_reg3 <- feols(income_diff ~ new_death_rate+merchants_all | fips | mpc_lag*revenue_diff ~ mpc_lag*ppp_dummy, iv_df,weights=iv_df$weighted_income)
summary(iv_reg3)

iv_reg4 <- feols(income_diff ~ new_death_rate+merchants_all | date_yw | mpc_lag*revenue_diff ~ mpc_lag*ppp_dummy, iv_df,weights=iv_df$weighted_income)
summary(iv_reg4)

iv_reg5 <- feols(income_diff ~ new_death_rate+merchants_all | fips + date_yw | mpc_lag*revenue_diff ~ mpc_lag*ppp_dummy, iv_df,weights=iv_df$weighted_income)
summary(iv_reg5)

iv_reg6 <- feols(income_diff ~ new_death_rate+merchants_all | fips | mpc_lag*revenue_diff ~ mpc_lag*ppp_impute, iv_df,weights=iv_df$weighted_income)
summary(iv_reg6)

iv_reg7 <- feols(income_diff ~ new_death_rate+merchants_all | date_yw | mpc_lag*revenue_diff ~ mpc_lag*ppp_impute, iv_df,weights=iv_df$weighted_income)
summary(iv_reg7)

iv_reg8 <- feols(income_diff ~ new_death_rate+merchants_all | fips + date_yw | mpc_lag*revenue_diff ~ mpc_lag*ppp_impute, iv_df,weights=iv_df$weighted_income)
summary(iv_reg8)

```

```{r}
library(ggplot2)

graph_df <- revenue_gdp_reg_df %>% group_by(fips) %>% summarise(mod = list(lm(revenue_diff ~ gdp_diff+new_case_rate+merchants_all)))%>%rowwise()

graph_df$coef <- lapply(graph_df$mod,function(x) x$coefficients[[2]])

gdp_graph <- left_join(income_revenue_reg_df, graph_df %>% select(coef,fips), by = c("fips")) %>% select(fips,coef,mpc,tot_pop,median) %>% distinct() %>% unnest(coef)  
mpc_mean <- gdp_graph %>% group_by(fips) %>% summarise(mean_mpc=mean(mpc))
gdp_graph <- left_join(gdp_graph, mpc_mean, by = c("fips")) %>% select(-mpc) %>% distinct() %>% mutate(weighted_pop=tot_pop/sum(gdp_graph$tot_pop)) %>% mutate(weighted_income=median/sum(gdp_graph$median)) %>% mutate(income_weight_mpc=mean_mpc*weighted_income) %>% mutate(income_weight_coef=coef*weighted_income)

gdp_graph$non_zero_mpc <- gdp_graph$mean_mpc
gdp_graph$non_zero_mpc[gdp_graph$non_zero_mpc == 0] <- NA
 
#ggplot(gdp_graph, aes(x=income_weight_mpc, y=income_weight_coef)) + geom_point()+geom_smooth(method=lm)

ggplot(gdp_graph, aes(x=non_zero_mpc, y=coef)) + geom_point()+geom_smooth(method=lm)
#gdp_graph <- gdp_graph %>% keep( ~ !is.null(.) )


```


```{r}

gdp_revenue_reg0 <- feols(revenue_diff ~ mpc_lag*gdp_diff , revenue_gdp_reg_df)
summary(gdp_revenue_reg0,"hetero")

gdp_revenue_reg1 <- feols(revenue_diff ~ mpc_lag*gdp_diff, revenue_gdp_reg_df, weights = revenue_gdp_reg_df$weighted_income)
summary(gdp_revenue_reg1,"hetero")

gdp_revenue_reg2 <- feols(revenue_diff ~ new_death_rate+merchants_all+mpc_lag*gdp_diff, revenue_gdp_reg_df)
summary(gdp_revenue_reg2,"hetero")

gdp_revenue_reg3 <- feols(revenue_diff ~ new_death_rate+merchants_all+mpc_lag*gdp_diff | date_yw, revenue_gdp_reg_df)
summary(gdp_revenue_reg3,"hetero")

gdp_revenue_reg4 <- feols(revenue_diff ~ new_death_rate+merchants_all+mpc_lag*gdp_diff | fips + date_yw, revenue_gdp_reg_df)
summary(gdp_revenue_reg4,"cluster")

p_gdp <- ggplot(revenue_gdp_reg_df, aes(x=gdp_diff)) + 
  geom_histogram()

revenue_coef=coef(gdp_revenue_reg3, 'mpc_lag:gdp_diff')
coef_df <- coef_df %>% mutate(business_elasticity=mpc_lag*revenue_coef)

```

```{r}
library(simPop)
cov_df <- coef_df
cov_df <- cov_df[!is.na(cov_df$mpc), ]
cov_df <- cov_df[!is.na(cov_df$income_region), ]
cov_df <- cov_df[!is.na(cov_df$income_elasticity), ]
cov_df <- cov_df[!is.na(cov_df$business_elasticity), ]
cov_df <- ungroup(cov_df)
cov_df <- cov_df %>% mutate(cov_weight=income_region/sum(income_region,na.rm=TRUE)) %>% mutate(product=income_elasticity*business_elasticity)
# cov <- cov.wt(cov_df %>% select(mpc,product), wt = cov_weight, cor = FALSE, center = TRUE,method = "unbiased")

cov <- cov.wt(cov_df[c("mpc", "product")], wt = cov_df$cov_weight, cor = FALSE, center = TRUE,method = "unbiased")
cov_unweight <- cov.wt(cov_df[c("mpc", "product")], cor = FALSE, center = TRUE,method = "unbiased")

p_mpc <- ggplot(cov_df, aes(x=mpc)) + 
  geom_histogram()
p_mpc_lag <- ggplot(cov_df, aes(x=mpc_lag)) + 
  geom_histogram()
p_income_elas <- ggplot(cov_df, aes(x=income_elasticity)) + 
  geom_histogram()
p_business_elas <- ggplot(cov_df, aes(x=business_elasticity)) + 
  geom_histogram()

cov_unweight$cov
cov$cov

```
```{r}
# produce descriptive stat table

descriptive_stat_df<-revenue_gdp_reg_df %>% ungroup() %>% left_join(select(income_revenue_reg_df,fips,date_yw),by=(c('fips','date_yw'))) %>%  select(fips,annual_income,income_region,income_diff,mpc,revenue_diff,gdp_diff,merchants_all,new_death_rate)
stargazer(as.data.frame(descriptive_stat_df), type = "latex", title="Descriptive statistics", digits=1, out="table1.txt",covariate.labels=c("Annual individual income","Weekly county income","Weekly income percentage change","County MPC","Weekly revenue percentage change","Weekly GDP percentage change","Num. of small business openings (rel. to Jan 2020)","New COVID-19 death rate"),omit.summary.stat = c('p25','p75','min','max'))

```

```{r}
# produce regression result tables

setFixest_dict(c(mpc_lag = "Lag MPC", revenue_diff = "Weekly revenue percentage change",new_death_rate = "New COVID-19 death rate", merchants_all = "Num. of small business openings",date_yw='Time',fips='County',income_diff='Weekly income percentage change',gdp_diff='Weekly GDP percentage change'))

s1 = summary(income_revenue_reg0, "hetero")
s2 = summary(income_revenue_reg1, "hetero")
s3 = summary(income_revenue_reg2, cluster = ~ fips)
s4 = summary(income_revenue_reg3, cluster = ~ fips)
table<-etable(list(s1, s2, s3, s4), order = c("x", "!Inter") ,style.tex = style.tex(depvar.title = "", fixef.title = "", fixef.suffix = " fixed effect"),tex = TRUE)
   
g1 = summary(gdp_revenue_reg0, "hetero")
#g2 = summary(gdp_revenue_reg2, "hetero")
g3 = summary(gdp_revenue_reg3, "hetero")
g4 = summary(gdp_revenue_reg4, cluster = ~ fips)
table2<-etable(list(g1, g3, g4), order = c("x", "!Inter") ,style.tex = style.tex(depvar.title = "", fixef.title = "", fixef.suffix = " fixed effect"),tex = TRUE)

```
```{r}

p_business_ela <- ggplot(cov_df, aes(x=business_elasticity)) + 
  geom_histogram()

p_income_ela <- ggplot(cov_df, aes(x=income_elasticity)) + 
  geom_histogram()

library(usmap) 
plot_df <- coef_df
plot_df <- plot_df %>% group_by(fips) %>% mutate(average_mpc=mean(mpc)) %>% mutate(average_income=mean(annual_income))
map <- plot_usmap(data = plot_df, values = "mpc", regions="counties", color = "blue",size=0.15) + scale_fill_continuous(low = "white", high = "blue", name = "Average Marginal Propensity to Consume", label = scales::comma) + 
  theme(legend.position = "right")

small_plot_df1 <- revenue_gdp_reg_df %>%
  filter(year == 2020 & week == 2) %>% ungroup() %>%
  select(fips, revenue1=revenue_all) 
small_plot_df2 <- revenue_gdp_reg_df %>%
  filter(year == 2021 & week == 4) %>% ungroup()%>%
  select(fips, revenue2=revenue_all)
small_plot_df<- small_plot_df2 %>% left_join(small_plot_df1, on=fips) %>% mutate(revenue_span=revenue2-revenue1)

small_biz_map <- plot_usmap(data = small_plot_df, values = "revenue_span", regions="counties", color = "blue",size=0.15) + scale_fill_continuous(low = "white", high = "blue", name = "Average Marginal Propensity to Consume", label = scales::comma) + 
  theme(legend.position = "right")
```


```{r}
quantile_df <- revenue_gdp_reg_df[!is.na(revenue_gdp_reg_df$revenue_all), ] %>% ungroup()

quantile_df <- quantile_df %>%
  group_by(date_yw) %>%
  summarize(quant25 = quantile(revenue_all, probs = 0.25),
            quant50 = quantile(revenue_all, probs = 0.50),
            quant75 = quantile(revenue_all, probs = 0.75)) %>% ungroup()

quantile_df$date_yw<-gsub("(\\d{4})(\\d{2})$","\\1-\\2",quantile_df$date_yw)

quantile_df$date <- as.Date(paste(quantile_df$date_yw, "5", sep = "-"), "%Y-%W-%u")
quantile_df$year_month <- format(quantile_df$date, "%Y-%m")

quantile_df_long <- gather(quantile_df, quant, value, quant25:quant75, factor_key=TRUE)

quantile_plot <- ggplot(data=quantile_df_long, aes(x=date_yw, y=value, group=quant)) +
  geom_line(aes(color=quant))+
  geom_point(aes(color=quant))+scale_color_grey() + theme_classic()


date_yw_inds <- seq(1,length(quantile_df$date_yw),by=4)

quantile_error_plot<-ggplot(quantile_df, aes(x=factor(date_yw), y=quant50, label=year_month),color="blue") + 
    geom_errorbar(aes(ymin=quant25, ymax=quant75),color="azure4", width=0.5) +
    geom_point(color="darkslategrey")+xlab("Year-Month") + scale_x_discrete(breaks=quantile_df$date_yw[date_yw_inds], labels = quantile_df$year_month[date_yw_inds]) +
    ylab("Small business revenue change (%)") +theme_minimal()+theme(axis.text.x = element_text(angle = 40,  hjust=1))
    

# error bar with sd
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}

error_plot_df <- data_summary(revenue_gdp_reg_df, varname="revenue_all", groupnames="date_yw")

error_plot<-ggplot(error_plot_df, aes(x=date_yw, y=revenue_all)) + 
    geom_errorbar(aes(ymin=revenue_all-sd, ymax=revenue_all+sd), width=.1) +
    geom_line() + geom_point()+
   scale_color_brewer(palette="Paired")+theme_minimal()

```

```{r}

elasticity_summary<-coef_df %>% ungroup() %>% select(income_elasticity,business_elasticity,mpc)
stargazer(as.data.frame(elasticity_summary), type = "latex", title="Descriptive statistics", digits=1,omit.summary.stat = c('min','max','p25','p75'))
#covariate.labels=c("Annual individual income","Weekly county income","Weekly income percentage change","County MPC","Weekly revenue percentage change","Weekly GDP percentage change","Num. of small business openings (rel. to Jan 2020)","New COVID-19 death rate")
```










